---
title: "ORA-KEGG ANALYSIS REPORT"
date: "`r format(Sys.time(), '%d %B %Y %H:%M:%S')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION
The following report summarizes the pathway analysis performed in the application [GSApp](https://github.com/albertme0308/GSApp).<br>
Pathway analysis method **ORA-KEGG**: Over Representation Analysis with annotation KEGG.<br>


## DATA LOADED
Below are the initial data description.<br>
The name of the loaded file is: **`r nombre_archivo()`**.<br>
Selected organism: **`r input$organismo`**.<br>
Gene ID: **`r input$identificador`**.<br>
Universe o Background: **`r input$universo1`**.<br>
Selected subset of genes: **`r input$genes1`**.<br>
Data related to gene subsetting:
```{r}
if(input$genes1=="Filter Toptable"){
  mensaje <- paste0("adj.P.Val <", as.numeric(input$adjpval1), 
                    ", logFC >", input$logFC1, 
                    ", Expression:", input$regulacion1)
  print(mensaje)
}else{print("Does not apply")}
```

Subset of genes selected for the analysis (10 first elements):
```{r}
head(genes(), 10)
paste("The subset of genes has a total of", length(genes()), "elements")
```


## ANALYSIS CONFIGURATION
The selected parameters for the analysis are described below.<br>
minGSSize: **`r input$minGSSize2`**.<br>
maxGSSize: **`r input$maxGSSize2`**.<br>
pAdjustMethod: **`r input$pAdjustMethod2`**.<br>
pvalueCutoff: **`r as.numeric(input$pvalue2)`**.<br>
qvalueCutoff: **`r as.numeric(input$qvalue2)`**.<br>


## ANALYSIS RESULTS
Table ORA-KEGG analysis (10 first categories):

```{r}
head(orakegg_results()[,2:7], 10)
paste("The number of categories obtained in the analysis is", nrow(orakegg_results()))
```


## RESULTS VISUALIZATION

**Upsetplot:**

```{r}
upsetplot(ora_kegg())
```

**Dotplot:**

```{r}
dotplot(ora_kegg(), showCategory = input$showcat_dotplot2, font.size=input$fontsize_dotplot2)
```

**Barplot:**

```{r}
barplot(ora_kegg(), showCategory = input$showcat_barplot2, font.size=input$fontsize_barplot2)
```

**Enrichment Map:**

Color category: **`r input$color_enmap2`**.<br>
```{r}
ora_kegg_sim2<-pairwise_termsim(ora_kegg())
emapplot(ora_kegg_sim2, showCategory = input$showcat_enmap2, color=input$color_enmap2, cluster.params=list(cluster=TRUE, legend=TRUE))
```

**Category Netplot:**

```{r}
cnetplot(ora_kegg(), showCategory = input$showcat_cnetplot2, color.params =list(foldChange =genes()))
```

**Pathway**<br>
Select the pathway in the application and browse it on the KEGG website.

**Tree plot:**

Color category: **`r input$color_tp2`**.<br>
Clustering method: **`r input$method_tp2`**.<br>
```{r}
ora_kegg_sim_tp2<-pairwise_termsim(ora_kegg())
treeplot(ora_kegg_sim_tp2, showCategory = input$showcat_tp2, color=input$color_tp2, cluster.params=list(method=input$method_tp2))
```


## VERSIONS

Versions of the packages used in the analysis:
```{r }
paste("clusterProfiler", packageVersion("clusterProfiler"))
paste("enrichplot", packageVersion("enrichplot"))
paste("ReactomePA", packageVersion("ReactomePA"))
paste("ggplot2", packageVersion("ggplot2"))
paste("DOSE", packageVersion("DOSE"))
paste("pathview", packageVersion("pathview"))
paste("SPIA", packageVersion("SPIA"))
paste("org.Mm.eg.db", packageVersion("org.Mm.eg.db"))
paste("org.Hs.eg.db", packageVersion("org.Hs.eg.db"))
paste("org.Rn.eg.db", packageVersion("org.Rn.eg.db"))
```
