---
title: "GSEA-KEGG ANALYSIS REPORT"
date: "`r format(Sys.time(), '%d %B %Y %H:%M:%S')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION
The following report summarizes the pathway analysis performed in the application [GSApp](https://github.com/albertme0308/GSApp).<br>
Pathway analysis method **GSEA-KEGG**: Gene Set Enrichment Analysis with annotation KEGG.<br>


## DATA LOADED
Below are the initial data description.<br>
The name of the loaded file is: **`r nombre_archivo()`**.<br>
Selected organism: **`r input$organismo`**.<br>
Gene ID: **`r input$identificador`**.<br>
Ranking variable: **`r input$parametro`**.<br>

Gene list selected for the analysis (10 first elements):
```{r}
head(genes_gsea(), 10)
paste("Gene list has a total of", length(genes_gsea()), "elements")
```


## ANALYSIS CONFIGURATION
The selected parameters for the analysis are described below.<br>
minGSSize: **`r input$minGSSize5`**.<br>
maxGSSize: **`r input$maxGSSize5`**.<br>
pAdjustMethod: **`r input$pAdjustMethod5`**.<br>
pvalueCutoff: **`r as.numeric(input$pvalue5)`**.<br>
eps: **`r as.numeric(input$eps5)`**.<br>
by: **`r input$by5`**.<br>


## ANALYSIS RESULTS
Table GSEA-KEGG analysis (10 first categories):

```{r}
head(gseakegg_results()[,2:7], 10)
paste("The number of categories obtained in the analysis is", nrow(gseakegg_results()))
```


## RESULTS VISUALIZATION

**Upsetplot:**

```{r}
upsetplot(gsea_kegg())
```

**Dotplot:**

Differential expression: **`r input$expresion5`**.<br>
```{r}
if (input$expresion5=="Global"){
        dotplot(gsea_kegg(), showCategory = input$showcat_dotplot5, font.size=input$fontsize_dotplot5)
      }else if (input$expresion5=="Differential"){
        dotplot(gsea_kegg(), showCategory = input$showcat_dotplot5, font.size=input$fontsize_dotplot5, split=".sign") + facet_grid(.~.sign)
      }
```

**Enrichment Map:**

Color variable: **`r input$color_enmap5`**.<br>
```{r}
gsea_kegg_sim5<-pairwise_termsim(gsea_kegg())
emapplot(gsea_kegg_sim5, showCategory = input$showcat_enmap5, color=input$color_enmap5, cluster.params=list(cluster=TRUE, legend=TRUE))
```

**Category Netplot:**

```{r}
cnetplot(gsea_kegg(), showCategory = input$showcat_cnetplot5, color.params =list(foldChange =genes_gsea()))
```

**Ridgeplot:**

Color variable: **`r input$fill_ridgeplot5`**.<br>
```{r}
ridgeplot(gsea_kegg(), showCategory = input$showcat_ridgeplot5, label_format = input$label_format_ridgeplot5, fill=input$fill_ridgeplot5)+labs(x="enrichment distribution")
```

**GSEA plot:**

```{r}
gseaplot(gsea_kegg(), by="all", title=gsea_kegg()@result$Description[input$gseakegg_num5], geneSetID = input$gseakegg_num5)
```

**Pathway**<br>
Select the pathway in the application and browse it on the KEGG website.

**Tree plot:**

Color category: **`r input$color_tp5`**.<br>
Clustering method: **`r input$method_tp5`**.<br>
```{r}
gsea_kegg_sim_tp5<-pairwise_termsim(gsea_kegg())
treeplot(gsea_kegg_sim_tp5, showCategory = input$showcat_tp5, color=input$color_tp5, cluster.params=list(method=input$method_tp5))
```


## VERSIONS

Versions of the packages used in the analysis:
```{r }
paste("clusterProfiler", packageVersion("clusterProfiler"))
paste("enrichplot", packageVersion("enrichplot"))
paste("ReactomePA", packageVersion("ReactomePA"))
paste("ggplot2", packageVersion("ggplot2"))
paste("DOSE", packageVersion("DOSE"))
paste("pathview", packageVersion("pathview"))
paste("SPIA", packageVersion("SPIA"))
paste("org.Mm.eg.db", packageVersion("org.Mm.eg.db"))
paste("org.Hs.eg.db", packageVersion("org.Hs.eg.db"))
paste("org.Rn.eg.db", packageVersion("org.Rn.eg.db"))
```