---
title: "GSEA-REACTOME ANALYSIS REPORT"
date: "`r format(Sys.time(), '%d %B %Y %H:%M:%S')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION
The following report summarizes the pathway analysis performed in the application [GSApp](https://github.com/albertme0308/GSApp).<br>
Pathway analysis method **GSEA-REACTOME**: Gene Set Enrichment Analysis with annotation Reactome.<br>


## DATA LOADED
Below are the initial data description.<br>
The name of the loaded file is: **`r nombre_archivo()`**.<br>
Selected organism: **`r input$organismo`**.<br>
Gene ID: **`r input$identificador`**.<br>
Ranking variable: **`r input$parametro`**.<br>

Gene list selected for the analysis (10 first elements):
```{r}
head(genes_gsea(), 10)
paste("ne list has a total of", length(genes_gsea()), "elements")
```


## ANALYSIS CONFIGURATION
The selected parameters for the analysis are described below.<br>
minGSSize: **`r input$minGSSize6`**.<br>
maxGSSize: **`r input$maxGSSize6`**.<br>
pAdjustMethod: **`r input$pAdjustMethod6`**.<br>
pvalueCutoff: **`r as.numeric(input$pvalue6)`**.<br>
eps: **`r as.numeric(input$eps6)`**.<br>
by: **`r input$by6`**.<br>


## ANALYSIS RESULTS
Table GSEA-REACTOME analysis (10 first categories):
```{r}
head(gseareactome_results()[,2:7], 10)
paste("The number of categories obtained in the analysis is", nrow(gseareactome_results()))
```


## RESULTS VISUALIZATION

**Upsetplot:**

```{r}
upsetplot(gsea_reactome())
```

**Dotplot:**

Differential expression: **`r input$expresion6`**.<br>
```{r}
if (input$expresion6=="Global"){
        dotplot(gsea_reactome(), showCategory = input$showcat_dotplot6, font.size=input$fontsize_dotplot6)
      }else if (input$expresion6=="Differential"){
        dotplot(gsea_reactome(), showCategory = input$showcat_dotplot6, font.size=input$fontsize_dotplot6, split=".sign") + facet_grid(.~.sign)
      }
```

**Enrichment Map:**

Color variable: **`r input$color_enmap6`**.<br>
```{r}
gsea_reactome_sim6<-pairwise_termsim(gsea_reactome())
emapplot(gsea_reactome_sim6, showCategory = input$showcat_enmap6, color=input$color_enmap6, cluster.params=list(cluster=TRUE, legend=TRUE))
```

**Category Netplot:**

```{r}
cnetplot(gsea_reactome(), showCategory = input$showcat_cnetplot6, color.params =list(foldChange =genes_gsea()))
```

**Ridgeplot:**

Color variable: **`r input$fill_ridgeplot6`**.<br>
```{r}
ridgeplot(gsea_reactome(), showCategory = input$showcat_ridgeplot6, label_format = input$label_format_ridgeplot6, fill=input$fill_ridgeplot6)+labs(x="enrichment distribution")
```

**GSEA plot:**

```{r}
gseaplot(gsea_reactome(), by="all", title=gsea_reactome()@result$Description[input$gseareactome_num6], geneSetID = input$gseareactome_num6)
```

**Category Pathway:**

```{r}
viewPathway(gsea_reactome()@result$Description[input$pathway_num6], readable=TRUE)
```

**Tree plot:**

Color variable: **`r input$color_tp6`**.<br>
Clustering method: **`r input$method_tp6`**.<br>
```{r}
gsea_reactome_sim_tp6<-pairwise_termsim(gsea_reactome())
treeplot(gsea_reactome_sim_tp6, showCategory = input$showcat_tp6, color=input$color_tp6, cluster.params=list(method=input$method_tp6))
```


## VERSIONS

Versions of the packages used in the analysis:
```{r }
paste("clusterProfiler", packageVersion("clusterProfiler"))
paste("enrichplot", packageVersion("enrichplot"))
paste("ReactomePA", packageVersion("ReactomePA"))
paste("ggplot2", packageVersion("ggplot2"))
paste("DOSE", packageVersion("DOSE"))
paste("pathview", packageVersion("pathview"))
paste("SPIA", packageVersion("SPIA"))
paste("org.Mm.eg.db", packageVersion("org.Mm.eg.db"))
paste("org.Hs.eg.db", packageVersion("org.Hs.eg.db"))
paste("org.Rn.eg.db", packageVersion("org.Rn.eg.db"))
```