---
title: "GSEA-GO ANALYSIS"
date: "`r format(Sys.time(), '%d %B %Y %H:%M:%S')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION
The following report summarizes the pathway analysis performed in the application [GSApp](https://github.com/albertme0308/GSApp).<br>
Pathway analysis method **GSEA-GO**: Gene Set Enrichment Analysis with annotation Gene-Ontology.<br>


## DATA LOADED
Below are the initial data description.<br>
The name of the loaded file is: **`r nombre_archivo()`**.<br>
Selected organism: **`r input$organismo`**.<br>
Gene ID: **`r input$identificador`**.<br>
Ranking variable: **`r input$parametro`**.<br>

Gene list selected for the analysis (10 first elements):
```{r}
head(genes_gsea(), 10)
paste("Gene list has a total of", length(genes_gsea()), "elements")
```

## ANALYSIS CONFIGURATION
The selected parameters for the analysis are described below.<br>
ont: **`r input$ont4`**.<br>
minGSSize: **`r input$minGSSize4`**.<br>
maxGSSize: **`r input$maxGSSize4`**.<br>
pAdjustMethod: **`r input$pAdjustMethod4`**.<br>
pvalueCutoff: **`r as.numeric(input$pvalue4)`**.<br>
eps: **`r as.numeric(input$eps4)`**.<br>
by: **`r input$by4`**.<br>
A method is used to reduce redundancy?: **`r input$simplify4`**.<br>


## ANALYSIS RESULTS
Table GSEA-GO analysis (10 first categories):

```{r}
head(gseago_results()[,2:7], 10)
paste("The number of categories obtained in the analysis is", nrow(gseago_results()))
```


## RESULTS VISUALIZATION

**Upsetplot:**

```{r}
upsetplot(gsea_go())
```

**Dotplot:**

Differential expression: **`r input$expresion4`**.<br>
```{r}
if (input$expresion4=="Global"){
      dotplot(gsea_go(), showCategory = input$showcat_dotplot4, font.size=input$fontsize_dotplot4)
    }else if (input$expresion4=="Differential"){
        dotplot(gsea_go(), showCategory = input$showcat_dotplot4, font.size=input$fontsize_dotplot4, split=".sign") + facet_grid(.~.sign)}
```

**Enrichment Map:**

Color variable: **`r input$color_enmap4`**.<br>
```{r}
gsea_go_sim4<-pairwise_termsim(gsea_go())
emapplot(gsea_go_sim4, showCategory = input$showcat_enmap4, color=input$color_enmap4, cluster.params=list(cluster=TRUE, legend=TRUE))
```

**GO plot:**

```{r}
goplot(gsea_go(), showCategory = input$showcat_goplot4)
```

**Category Netplot:**

```{r}
cnetplot(gsea_go(), showCategory = input$showcat_cnetplot4, color.params =list(foldChange =genes_gsea()))
```

**Ridgeplot:**

Color variable: **`r input$fill_ridgeplot4`**.<br>
```{r}
ridgeplot(gsea_go(), showCategory = input$showcat_ridgeplot4, label_format = input$label_format_ridgeplot4, fill=input$fill_ridgeplot4)+labs(x="enrichment distribution")
```

**GSEA plot:**

```{r}
gseaplot(gsea_go(), by="all", title=gsea_go()@result$Description[input$gseago_num4], geneSetID = input$gseago_num4)
```

**Tree plot:**

Color variable: **`r input$color_tp4`**.<br>
Clustering method: **`r input$method_tp4`**.<br>
```{r}
gsea_go_sim_tp4<-pairwise_termsim(gsea_go())
treeplot(gsea_go_sim_tp4, showCategory = input$showcat_tp4, color=input$color_tp4, cluster.params=list(method=input$method_tp4))
```


## VERSIONS

Versions of the packages used in the analysis:
```{r }
paste("clusterProfiler", packageVersion("clusterProfiler"))
paste("enrichplot", packageVersion("enrichplot"))
paste("ReactomePA", packageVersion("ReactomePA"))
paste("ggplot2", packageVersion("ggplot2"))
paste("DOSE", packageVersion("DOSE"))
paste("pathview", packageVersion("pathview"))
paste("SPIA", packageVersion("SPIA"))
paste("org.Mm.eg.db", packageVersion("org.Mm.eg.db"))
paste("org.Hs.eg.db", packageVersion("org.Hs.eg.db"))
paste("org.Rn.eg.db", packageVersion("org.Rn.eg.db"))
```