---
title: "SPIA ANALYSIS REPORT"
date: "`r format(Sys.time(), '%d %B %Y %H:%M:%S')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION
The following report summarizes the pathway analysis performed in the application [GSApp](https://github.com/albertme0308/GSApp).<br>
Pathway analysis method **SPIA**: Signaling-Pathway Impact Analysis with annotation KEGG.<br>


## DATA LOADED
Below are the initial data description.<br>
The name of the loaded file is: **`r nombre_archivo()`**.<br>
Selected organism: **`r input$organismo`**.<br>
Gene ID: **`r input$identificador`**.<br>
Universe o Background: **`r input$referencia7`**.<br>
Selected subset of genes: **`r input$genes7`**.<br>
Data related to gene subsetting:
```{r}
if(input$genes7=="Filter Toptable"){
  mensaje <- paste0("adj.P.Val <", as.numeric(input$adjpval7), 
                    ", logFC >", input$logFC7, 
                    ", Expression:", input$regulacion7)
  print(mensaje)
}else{print("Does not apply")}
```

Subset of genes selected for the analysis (10 first elements):
```{r}
head(genes_spia(), 10)
paste("The subset of genes has a total of", length(genes_spia()), "elements")
```


## ANALYSIS CONFIGURATION
The selected parameters for the analysis are described below.<br>
nB: **`r input$nB7`**.<br>


## ANALYSIS RESULTS
Table SPIA analysis (10 first categories):

```{r}
head(spia_results()[,1:12], 10)
paste("The number of categories obtained in the analysis is", nrow(spia_results()))
```


## RESULTS VISUALIZATION

**PlotP:**

Threshold: **`r input$threshold7`**.<br>
```{r}
plotP2(spia_kegg(), threshold=input$threshold7)
```

**Pathway SPIA**<br>
Select the pathway in the application and browse it on the KEGG website.


## VERSIONS

Versions of the packages used in the analysis:
```{r }
paste("clusterProfiler", packageVersion("clusterProfiler"))
paste("enrichplot", packageVersion("enrichplot"))
paste("ReactomePA", packageVersion("ReactomePA"))
paste("ggplot2", packageVersion("ggplot2"))
paste("DOSE", packageVersion("DOSE"))
paste("pathview", packageVersion("pathview"))
paste("SPIA", packageVersion("SPIA"))
paste("org.Mm.eg.db", packageVersion("org.Mm.eg.db"))
paste("org.Hs.eg.db", packageVersion("org.Hs.eg.db"))
paste("org.Rn.eg.db", packageVersion("org.Rn.eg.db"))
```